%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\begin{center}
    {\Huge \scshape Nitav Shah} \\ \vspace{1pt}
    Philadelphia, PA 19104 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 443-947-0663 ~ \href{mailto:shahnitav@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{shahnitav@gmail.com}} ~ 
    \href{https://linkedin.com/in/nitavshah/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/nitavshah}}  ~
    \href{https://github.com/shahnitav}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/shahnitav}}  ~
    \href{https://nitav.me}{\raisebox{-0.2\height}\faGlobe\
    \underline{nitav.me}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland}{Aug 2021 -- May 2023}
      {Master of Engineering in Cybersecurity, GPA: 3.93}{College Park, MD}
  \resumeSubHeadingListEnd
\vspace{-6pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Navrachana University}{Aug 2016 -- June 2020}
      {Bachelor of Technology in Computer Science and Engineering, CGPA: 8.67}{India}
  \resumeSubHeadingListEnd
\vspace{-12pt}
%------CERTIFICATES-------
\section{Certificates}
    %\resumeSubHeadingListStart
        \begin{itemize}
            \item CompTIA Security+ SY0-601 - CompTIA
            \vspace{-10pt}
            \item Investigation Theory - Applied Network Defense
        \end{itemize}
    %\resumeSubHeadingListEnd
\vspace{-18pt}

%------RELEVANT COURSEWORK-------
%\section{Relevant Coursework}
    %\resumeSubHeadingListStart
%        \begin{multicols}{4}
%            \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                \item\small Hacking of C Binaries
%                \item Networking Protocols
%                \item Penetration Testing
%                \item Network Security
%                \item Secure Operating System
%                \item Info. Security Tools
%                \item Computer Networks
%                \item Cloud Security
%            \end{itemize}
%        \end{multicols}
%        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Susquehanna International Group}{Jul 2023 -- Present}
      {Security Engineer}{Bala Cynwd, PA}
      \resumeItemListStart
        \resumeItem{Responding to security incidents monitored using SIEM/EDR, coordinating a cohesive response for escalated incidents involving in-depth analysis, containment, and remediation.}
        \resumeItem{Write new detections in the SIEM for the rapidly changing threat landscape by following current security trends, advisories, publications, and research.}
        \resumeItem{Deployed and manage log integration to QRadar SIEM using WEC, Sysmon, WinCollect from thousands of workstations and servers across more than 4 global sites.}
        \resumeItem{Architectured scanning and vulnerability management using Tenable.sc \& NMap to reduce the external attack surface.}
        \resumeItem{Developed a custom SOAR web application that performs queries, gathers intel, gets relevant information from the security stack, and provides custom workflows after an incident to help analysts investigate.}
        \resumeItem{Monitor for sensitive data leaving the environment using Forcepoint DLP while fine tuning it to reduce false positives.}
        \resumeItem{Automate, store, and maintain Threat Intelligence feeds and use them for threat hunting across the environment.}
      \resumeItemListEnd
    \resumeSubheading
      {University of Maryland}{Jun 2022 -- May 2023}
      {Graduate IT Assistant}{College Park, MD}
      \resumeItemListStart
        \resumeItem{Triage incoming tickets and provide technical support by resolving the incidents.}
        \resumeItem{Developed PowerShell scripts to automate system administration tasks reducing the ticket response time by 100\%.}
      \resumeItemListEnd
    \vspace{-2pt}
    \resumeSubheading
      {University of Maryland}{Jan 2022 -- May 2022}
      {Teaching Assistant}{College Park, MD}
      \resumeItemListStart
        \resumeItem{Partnered with Prof. Nirupam Roy to implement suitable lessons for CMSC417-Computer Networks for 70 students.}
      \resumeItemListEnd
    \vspace{-4pt}
    \resumeSubheading
      {Syncron}{Jul 2020 -- Jul 2021}
      {Software Engineer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Incorporated scripts using Python and Golang to automate QA Testing and perform Functionality and Load Testing.}
        \resumeItem{Utilized AWS Codepipeline \& Codebuild to provide a CI/CD solution that runs builds and generates reports.}
        \resumeItem{Lead the development of a cross-platform Chatbot using Golang and Python Boto3 library to carry out DevOps task on AWS Infrastructure from Microsoft Teams Bot Framework.}
     \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Homelab} $|$ \emph{VMWare, pfsense, Kali Linux, Windows Server, Splunk, VLAN}  $|$ \href{https://github.com/shahnitav/HomeLab-Setup}{\underline{Project Link}}}{June 2022}
     \resumeItemListStart
        \resumeItem{Built and maintain a lab to test, upskill, and maintain an enterprise-grade environment.The lab uses a Hypervisor, Pfsense, Security Onion, Splunk, Windows Server, Metasploitable machines, Kali Linux Attacker and more.}
     \resumeItemListEnd
      \vspace{-20pt}
    \resumeProjectHeading
      {\textbf{Go Port Scanner} $|$ \emph{Go, Network Scanning}  $|$ \href{https://github.com/shahnitav/Go-Port-Scanner}{\underline{Project Link}}}{April 2022}
      \resumeItemListStart
        \resumeItem{Developed a Port Scanner that uses multi-threading to scan multiple ports/hosts simultaneously using goroutines.}
      \resumeItemListEnd
     \vspace{-20pt}
      \resumeProjectHeading
          {\textbf{Advanced Exploitation Techniques for x86 Architecture} $|$ \emph{GDB, Assembly}  $|$ \href{https://gitfront.io/r/shahnitav/c524d0b3db1db73ae1f406265e8315b0b9b80c3e/advanced-exploitation-techniques-x86/}{\underline{Project Link}}}{December 2021}
         \resumeItemListStart
            \resumeItem{Used problem solving and reverse engineering to find the exploits for 10 binaries with ASLR turned on by exploiting vulnerabilities using Heap Buffer Overflows and Return Oriented Programming.}
            \resumeItem{Created shellcode \& deduced the NOP Slide required to overwrite the return address to point to the heap or bss regions.}
         \resumeItemListEnd
         \vspace{-20pt}
      \resumeProjectHeading
          {\textbf{Penetration Test} $|$ \emph{Privilege Escalation, Threat Hunting, Vulnerability Analysis} $|$ \href{https://gitfront.io/r/shahnitav/e3d67918719298da3b929039fce43ab2858932bb/penetration-testing-report/}{\underline{Project Link}}}{December 2021}
          \resumeItemListStart
            \resumeItem{Discovered exposed cloud credentials, configuration flaws and unpatched systems exploitable with critical CVE.}
            \resumeItem{Adapted a security posture improvement response strategy with guidelines to deploy security controls \& policies.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go, C, HTML/CSS, JavaScript, SQL, C\#, Bash, PowerShell} \\
     \textbf{Scanning}{: Nmap, Wireshark, Nessus Tenable, GDB, QRadar, Splunk, SOAR, Firewall Configuration, RBAC} \\
     \textbf{Exploitation}{: Burpsuite, Metasploit, MITRE ATT\&CK, Penetration Testing, Detection Engineering} \\
     \textbf{Technologies}{: AWS, Linux, Docker, Git, OAuth, LDAP, Azure, Cloud Infrastructure, TCP/IP, DNS, Active Directory} \\
     \textbf{Security}{: Incident Response, Forensic Analysis, Vulnerability Management, DLP, NIST CsF, ISO 27000, Security Controls} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
